Simulating Ultra High-Dimensional Multivariate Data Using the bigsimr R Package

### 2020-06-20 030-bigsimr-package.Rmd
move rslurm example to advanced use, make corr test simpler

```{r setup, eval = TRUE}
## bookdown::preview_chapter('030-bigsimr-package.Rmd')
## bookdown::render_book('index.html')
library(bigsimr)
```

## Specifying marginals

@@

## Specify correlation

@@

## Small sample

@@

## Scaling up N

@@

## Evaluation

```{r}
cor(x, method = 'spearman')
```

@@

## Easy cluster implementation through `rslurm`

@@

>>>>

## Basic use

```{r setup, eval = TRUE}
## setwd('~/Research/article_bigsimr/'); bookdown::preview_chapter('030-bigsimr-package.Rmd')
## bookdown::render_book('index.html')
library(bigsimr)
## reticulate::use_condaenv( 'bigsimr-cpu' )
```

### Specifying marginals

@@

### Specify correlation

@@

### Generating a few random vectors

@@

### Scaling up N to 1,000,000

@@

### Check the performance with fast correlation estimation

```{r}
bigsimr::fastCor(x, method = 'spearman')
```

@@

## Advanced use

### Using multicore

Using multicore is easy simply specify the number of cores.

### Simulation-based computation of correlation bounds

Using the Generate, sort, and correlate algorithm @Demirtas2011  and TAS issue

- use a large number of reps

```{r, computeBounds, echo = TRUE, eval=FALSE}
## Possibly bug? or configuration
## Error: segfault from C stack overflow on my Okapi bigsimr env 
rho_bounds <- bigsimr::computeCorBounds(margins = margins, type = 'spearman', cores = 1, reps = 1e5)
rho_bounds
```

### Using `bigsimr` on a computing cluster via `rslurm`

@@

Now, let's show off the real power of combining `bigsimr` and `rslurm` by simulating many correlation structures for these three marginals. The `rslurm::slumr_map` syntax mirrors the familiar `base::lapply` and `purrr::map` functions.

```{r rvecRslurmMap, echo=TRUE, eval=FALSE}
library(rslurm)
## a single call of rvec
## had to edit rslurm/templates/submit_sh.txt
## source ~/.bashrc
## conda activate bigsimr
## conda env config vars list
set.seed(06202020)
simReps <- 100
rhoList <- replicate( n = simReps, bigsimr::rcor(d = length(margins), constant_rho = TRUE), simplify=FALSE )
sjob <- slurm_map(x = rhoList,
                  f = rvec,
                  jobname = 'rvecMap',
                  n=1e6,
                  margins = margins,
                  type = "spearman",
                  nodes = 4,
                  cpus_per_node = 4,
                  submit = TRUE)

```

On a cluster carrying 24 nodes with 48 threads, these 100 jobs completed in about a minute. Let's evaluate the quality of simulation performance.

```{r rvecRslurmMapRes, echo=TRUE, eval=FALSE}
list.files('_rslurm_rvecMap', 'results')
res <- rslurm::get_slurm_out(sjob, outtype = 'raw')
rhoHats <- lapply( res, bigsimr::fastCor, method = 'spearman' )

resData <- NULL
simreps <- length(rhoHats)
for (i in 1:simreps){
    tmpRhoHat <- rhoHats[[i]]
    ## average together
    margins
    avgRhoHat <- tmpRhoHat[lower.tri(tmpRhoHat)]
    tmpPair <- paste0( "pair", apply( combn(x = length(margins), 2), 2, paste, collapse = "_" ) )
    tmpResData <- data.frame( simNum=i, rho=rhoList[[i]][1,2], rhoHat=tmpRhoHat[lower.tri(tmpRhoHat)], pair=tmpPair )
    resData <- rbind(resData, tmpResData)
}

## "wrangle" into a tibble
library(tidyverse)
res <- as_tibble(resData)
## save for viz
saveRDS( res, file = 'data/rvecRslurmMapRes.rds' )

## cleanup careful this deletes output also
## cleanup_files(sjob) 
```

```{r rvecRslurmMapFig, echo = TRUE, eval=TRUE, message=FALSE, warning=FALSE, out.width= '75%', fig.align='center', fig.cap='The continous marginal pairs exact reproduce the specified correlation whereas the discrete pairs (green nad blue) show a downward bias. Future work with employ a discrete adjusted procedures using *rescaling* on the traditional correlation coefficient.'}
library(tidyverse)

res <- readRDS( 'data/rvecRslurmMapRes.rds' )
res

res %>%
    ggplot( aes( x = rho, y = rhoHat, color = pair ) )  +
    geom_point() +
    geom_abline( slope = 1, intercept = 0 )
```

### 2020-06-20 050-some-applications.Rmd
draft rslurm section
move rslurm example to advanced use, make corr test simpler

Since many of the correlations are near zero, one could ask whether it is
possible that

```{r brcaSigmaTesting, echo=TRUE, eval=FALSE}

@@

## Simulation-based computation of correlation bounds

Using the Generate, sort, and correlate algorithm @Demirtas2011

```{r, computeBounds, echo = TRUE, eval=FALSE}

## simulation based
## devtools::install_github("adknudson/bigsimr", ref="develop")
library(bigsimr)
## ?rvec

d <- 5
rho <- rcor(d)
margins <- list(
    list("nbinom", size = 5, prob = 0.3),
    list("exp", rate = 4),
    list("binom", size = 5, prob = 0.7),
    list("norm", mean = 10, sd = 3),
    list("pois", lambda = 10)
)

params = margins
rho = rho
## cores = parallel::detectCores() - 1
cores = 2
reps = 1e3
type = "spearman"

## help(package="bigsimr")
rho_bounds <- computeCorBounds(params = margins, cores = cores, type = type, reps = reps)
rho_bounds
```

>>>>

Since many of the correlations are near zero, one could ask whether it is
possible that test the hypothesis that $H_0: R = R_0$.

```{r corrTest, echo=FALSE, eval=FALSE, include=FALSE}

@@
